---
title: "Equations"
output: html_document
bibliography: bibliography/artrend.bib
link-citations: yes
#output: bookdown::html_document2
#link-citations: yes
#pkgdown:
#  as_is: true
#vignette: >
#  %\VignetteIndexEntry{Equations}
#  %\VignetteEngine{knitr::rmarkdown}
#  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE,echo=F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo =F,message=F}
library(arfit)
```


\begin{align}
\tag{1}
  Y_t = \beta_0 + \beta_1 t + \epsilon_t  
\end{align}

---

\begin{align}
\tag{2}
\mathrm{L}\left( \underline{\theta}; \underline{y} \right )= \prod^n_{t=2} p\left(Y_t = y_t | Y_{t-1}=y_{t-1}\right)  p\left(Y_1=y_1 \right) 
\end{align}

---

\begin{align}
\tag{3}
logL\left( \underline{\theta}; \underline{y} \right ) = & -\frac{n}{2}log2\pi - nlog\sigma + \frac{1}{2}log(1-\phi^2) \\
&-\frac{1}{2\sigma^2}\left( (1-\phi^2)(y_1-\beta_0-\beta_1)^2 + \sum^n_{t=2}(y_t - \phi y_{t-1}-\beta_0(1-\phi^2) -t\beta_1 + \phi(t-1)\beta_1)^2 \right)  
\end{align}

---

\begin{align}
\tag{4}
\hat\sigma^2 = \frac{1}{n}\left( (1-\phi^2)(y_1-\beta_0-\beta_1)^2 + \sum^n_{t=2}(y_t - \phi y_{t-1}-\beta_0(1-\phi^2) - t\beta_1 + \phi(t-1)\beta_1)^2 \right) 
\end{align}

---

\begin{align}
\tag{5}
logL\left( \underline{\beta}, \phi; \underline{y} \right ) &= const. + \frac{1}{2}log(1-\phi^2) \\
&-\frac{n}{2}log\left( (1-\phi^2)(y_1-\beta_0-\beta_1)^2 + \sum^n_{t=2}(y_t - \phi y_{t-1}-\beta_0(1-\phi^2)-t\beta_1 + \phi(t-1)\beta_1)^2 \right) \\ 

&= const. + \frac{1}{2}log(1-\phi^2) \\
&-\frac{n}{2}log\left( (1-\phi^2)(y_1-X_1\underline{\beta})^2 + \sum^n_{t=2}(y_t - \phi y_{t-1}-X_t\underline{\beta} + \phi X_{t-1}\underline{\beta})^2 \right) 
\end{align}

---

\begin{align}
\tag{6}
logL\left( \underline{\beta}, \underline{\phi},\sigma; \underline{y} \right ) &= -\frac{n}{2}log(2\pi) -\frac{n}{2}log(\sigma^2) +\frac{1}{2}log \left|V_p^{-1} \right|
\\
&-\frac{1 }{2 \sigma^2} (\underline{y_p}-\underline{\mu_p})^T V_p^{-1}(\underline{y_p}-\underline{\mu_p}) \\

&- \frac{1}{2\sigma^2}\sum^n_{t=p+1} (y_t - c - \phi_1y_{t-1} - ... - \phi_p y_{t-p})^2 

\end{align}


where

$\left|V_p^{-1} \right|$ is determinant of inverted matrix $V_p$,

$\sigma^2V_p$ = variance-covariance matrix of order p,

$\underline{\mu_p} = X_p\underline{\beta}$, and

$X_p$ is the $p_{th}$ row of the design matrix corresponding to time t = p

$c$ = function of fitted terms $X_t\underline{\beta}$






